### 2021-07-12 博士/论文提交/adversarial_attack/TCSVT/response/response.tex

\noindent \textbf{5. The paper contains some grammar mistakes and typos, the authors need to improve it by double check.}

Thanks for your advice and we changed the errors in the manuscript:

Our perturbations also generalize well to SiamFC++-ShuffleNet, \textbf{in despite of} the customized components such as pointwise group convolution and channel shuffle operations in ShuffleNet. $\rightarrow$ Our perturbations also generalize well to SiamFC++-ShuffleNet, \textbf{despite} the customized components such as pointwise group convolution and channel shuffle operations in ShuffleNet.

SPARK computes incremental perturbations by using information from the past frames to perform targeted attacks \textbf{to} Siamese trackers. $\rightarrow$ SPARK computes incremental perturbations by using information from the past frames to perform targeted attacks \textbf{on} Siamese trackers.
